Data- and Systems Paper: Identifying Handicap Parking Spots for Event's Venues

### 2016-04-09 milestone1/paper/paper.tex
Entailment part

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}	
\usepackage{listings}
\usepackage{multicol}
\usepackage{hyperref}
\lstset{language=SQL,morekeywords={PREFIX,java,rdf,rdfs,url}}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\textwidth]{img/use-case-diagram.png}
	\caption{Use case diagram showing how potential users can use the application created in this project.}
	\label{fig:use-case}
\end{figure}

@@

\subsection{Theaters, Museums and Galleries Dataset}
The Theaters and the Museums and Galleries datasets contain information about events happening in these types of venues. The datasets integrate easily since the both share the following main features:

@@

We created four classes: Event, Venue, Parking Slot and Location, of which the first three were defined by us and the last one was defined as a subclass of dbepedia's Location class. The Theaters and Museums and Galleries datasets were turned into Events containing Venues and Locations, while the Parking Slots dataset turned into Parking Slots with Locations. As shown, the common factor integrating the data is the Location class.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{img/vocab-graph.jpg}
	\caption{Visualization of the Ontology graph}
	\label{fig:vocabulary}
\end{figure}

To populate the database with instances, the JSON files were read and transformed into RDF triples using a python script. A sample instance is shown in Figure \ref{fig:instance}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{img/vocab-graph.jpg}
	\caption{Visualization of the Ontology graph}
	\label{fig:instance}
\end{figure}

The database is stored in \href{http://stardog.krw.d2s.labs.vu.nl/#/databases/group6}{this} Stardog server

We created three named graphs: \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/theaters}{Theaters}, \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/museums}{Museums} and \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/parking-slots}{Parking slots}.

\section{Semantic considerations}
% In the 2nd and 3rd lectures we introduced formal Semantics for RDF, RDFS and SPARQL. Please use your own knowledge graph to give some (simple) examples for entailment. Choose a subgraph G (feel free to adapt it if needed) and explain what it stands for, and what the intended meaning is. Given the problem and use-case you have in mind, how do the examples of entailment contribute to a solution?
Event is linked to a venue. Venue and parking slots are linked to locations
John knows the venue
Peter knows the event

\subsection{RDF and RDFS entailment}
% Give a small graph G' which is entailed by your subgraph G. Feel free to use the same G' that you want to use in your SPARQL query later. Explain why G' is entailed (this is really simple).

@@

\subsection{SPARQL}
% Give a SPARQL query that provides different answers on the basis of interpreting the knowledge graph with an RDF entailment regime as opposed to an RDFS regime, and explain why you get different answers.

\begin{lstlisting}[captionpos=b, caption=SPARQL query, label=lst:sparql,
basicstyle=\ttfamily,frame=bt]
prefix rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
prefix owl: <http://www.w3.org/2002/07/owl#>
prefix xsd: <http://www.w3.org/2001/XMLSchema#>
prefix rdfs: <http://www.w3.org/2000/01/rdf-schema#>

prefix : <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>
prefix data: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/>
prefix geo: <http://www.w3.org/2003/01/geo/wgs84_pos#>
prefix math: <http://www.w3.org/2005/xpath-functions/math#>
prefix dbo: <http://dbpedia.org/ontology/>

@@

\section{Discussion}
% Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
% Present a screenshot of a mock-up or working (preferred!) version of your system an describe what it does.
% Argue why the preceding sections show that your solution (partially) solves the problem you introduced in the introduction.

>>>>

\usepackage{url}
\usepackage{graphicx, colortbl}
\usepackage{amsmath,amssymb}	
\usepackage{listings}
\usepackage{multicol}
\usepackage{hyperref}
\lstset{language=SQL,morekeywords={PREFIX,java,rdf,rdfs,url}}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=.7\textwidth]{img/use-case-diagram.png}
	\caption{Use case diagram showing how potential users can use the application created in this project.}
	\label{fig:use-case}
\end{figure}

@@

\subsection{Theaters, Museums and Galleries Dataset}
The Theaters and the Museums and Galleries datasets contain information about events happening in these types of venues, as well as the details of the location of the venues. The datasets are comparable since the both share the following main features:

@@

We created four classes: Event, Venue, Parking Slot and Location, of which the first three were defined by us and the last one was defined as a subclass of dbepedia's Location class. The Theaters and Museums and Galleries datasets were turned into Events linked to Venues, and Venues linked Locations, while the Parking Slots dataset turned into Parking Slots linked to Locations. As shown, the common factor integrating the data is the Location class.

\begin{figure}[h]
	\centering
	\includegraphics[width=.7\textwidth]{img/vocab-graph.jpg}
	\caption{Visualization of the Ontology graph}
	\label{fig:vocabulary}
\end{figure}

To populate the database with instances, the JSON files were read and transformed into RDF triples using a python script. A sample instance is shown in Figure \ref{fig:instance}.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{img/knowledge-graph-example.png}
	\caption{Sample instance for a Venue "Galerie Sous-Terre" with specific property Location}
	\label{fig:instance}
\end{figure}

The database is stored in \href{http://stardog.krw.d2s.labs.vu.nl/#/databases/group6}{this} Stardog server and contains around 17 000 triples.

%We created three named graphs: \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/theaters}{Theaters}, \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/museums}{Museums} and \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/parking-slots}{Parking slots}.

\section{Semantic considerations}
% In the 2nd and 3rd lectures we introduced formal Semantics for RDF, RDFS and SPARQL. Please use your own knowledge graph to give some (simple) examples for entailment. Choose a subgraph G (feel free to adapt it if needed) and explain what it stands for, and what the intended meaning is. Given the problem and use-case you have in mind, how do the examples of entailment contribute to a solution?
In our use cases, the main goal if for a user to find a parking slots based on the event they want to attend. To do so, we use the common property location.However, the location of an event is not explicit, so we need to infer it.

Hereby we only consider the subgraph containing Events, Venues and Locations to illustrate how entailment enriches our knowledge.

\subsection{RDF and RDFS entailment}
% Give a small graph G' which is entailed by your subgraph G. Feel free to use the same G' that you want to use in your SPARQL query later. Explain why G' is entailed (this is really simple).
We asserted that Events take place in a Venue, and we also asserted that Venues have a Location. Thus it follows that Events happen in a Location.

The logical entailment rules are shown in the next argument:

\begin{center}
	\begin{tabular}{c@{\,}l@{}} 
  	& \textit{:Event 		:venue 				?$o_1$} \\
  	& \textit{?$o_1$ 		rdfs:type 			:Venue} \\   
  	& \textit{:Venue 		:location 			?$o_2$} \\ 
  	& \textit{?$o_2$ 		rdfs:type 			:Location} \\ 
  	& \textit{:Location		rdfs:subClassOf 	dbo:Location} \\
  	  	\arrayrulecolor{blue} \cline{2-2}
  	$\therefore$         
  	& \textit{:Event 		:location 				?$o_2$} \\
  	\end{tabular}
\end{center}

@@

\subsection{SPARQL}
% Give a SPARQL query that provides different answers on the basis of interpreting the knowledge graph with an RDF entailment regime as opposed to an RDFS regime, and explain why you get different answers.
The RDF schema would not be sufficient for our application to provide any results when a user knows the Event name but not the Venue.

RDFS provides us with a way to link Events and Locations. Thus, we can query Parking Slots that are related to that specific Location. We do this by retrieving all Parking Slots Locations and doing a geometrical comparison to the required Event Location. The query is shown in the Appendices.

\section{Discussion}
% Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
% Present a screenshot of a mock-up or working (preferred!) version of your system an describe what it does.
% Argue why the preceding sections show that your solution (partially) solves the problem you introduced in the introduction.
In this work we successfully transformed public data from the Amsterdam Municipality into and RDF schema. Furthermore, we created a model that enables us to integrate two different datasets: Theater and Museum and Galleries events, and parking Slots. Thanks to the power of RDFS we entail implicit knowledge about database, which allows us to query it and obtain useful information for the use cases explained in Section 2.

Our solution is capable of retrieving Parking Slots nearby a location. It saves time to the user since he does not need to know the location of the Venue and can go directly from knowing the event name to a convenient spot to park his car.

The web application may be improved by provided extended support. New queries may be added. %TODO finish this

\newpage
\appendix
\section{Prefixes used}

$rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns>$ \\
$owl: <http://www.w3.org/2002/07/owl>$ \\
$xsd: <http://www.w3.org/2001/XMLSchema>$ \\
$rdfs: <http://www.w3.org/2000/01/rdf-schema>$ \\
$: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>$ \\
$data: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/>$ \\
$geo: <http://www.w3.org/2003/01/geo/wgs84\_pos>$ \\
$math: <http://www.w3.org/2005/xpath-functions/math>$ \\
$dbo: <http://dbpedia.org/ontology/>$

\section{SQL Queries}

\begin{lstlisting}[captionpos=b, caption=SPARQL query for getting parking spots close to Podium Mozaiek (sorted by distance), label=lst:sparql,
basicstyle=\ttfamily,frame=bt]

@@
